Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-27 lloveras_2020.tex
cambio de graficos, uno nuevo agregado, otro eliminado

Once the LDEM is determined at each voxel, the average squared electron density $\langle N_e^2 \rangle$ and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,
\begin{eqnarray}\label{momento1}
 N_{e,i}^2 &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
\label{momento2}
 T_{\textrm{m},i}   &=& \frac{1}{N_{e,i}^2}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
\end{eqnarray}

@@

@@

\textcolor{red}{
*Para las piernas trazadas que cumplen  |pearson de temp| > 0.5 se calcularon los gradientes de temp que cumplen test de hipotesis. Estos gradientes se muestran en la Figura \ref{gradientes} para las 3 regiones definidas para ambas rotaciones. Esto muestra up y down loops.
OBS: esto da pie a hablar y proponer mejoras en la conversion de modos de alfven. citar paper fede.
*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel). In solid lines DEMT traced data and in dashed lines AWSoM data.}
\label{gradientes}
\end{center}
\end{figure}

@@

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

>>>>

Once the LDEM is determined at each voxel, the average squared electron density $\langle N_e^2 \rangle$ and the electron mean temperature $T_\textrm{m}$ in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,
\begin{eqnarray}\label{momento1}
 \langle N_{e,i}^2 \rangle &=& \int\,\textrm{d}T\,\LDEM_i(T),\label{Ne} \\ 
\label{momento2}
 T_{\textrm{m},i}   &=& \frac{1}{\langle N_{e,i}^2 \rangle}\,\int\,\textrm{d}T\,T\,\LDEM_i(T),\label{Tm} 
\end{eqnarray}

@@

\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}

@@

\textcolor{red}{
*Para las piernas trazadas que cumplen  |pearson de temp| > 0.5 se calcularon los gradientes de temp que cumplen test de hipotesis. Estos gradientes se muestran en la Figura \ref{gradientes} para las 3 regiones definidas para ambas rotaciones. Esto muestra up y down loops.
OBS: esto da pie a hablar y proponer mejoras en la conversion de modos de alfven. citar paper fede.
%*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
%\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II %(in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel). In solid lines DEMT traced data and in dashed lines AWSoM data.}
%\label{gradientes}
%\end{center}
%\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels). for CR-2082. DEMT results of CR2082 are shown in blue while those of CR2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}
\label{histos_2082}
\end{center}
\end{figure}
